---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ReproduceRapidMonitoring

<!-- badges: start -->
<!-- badges: end -->

The goal of this package is to reproduce the paper "Rapid monitoring for ecological persistence" by Chuliang Song, Benno Simmons, Marie-Josée Fortin, Andrew Gonzalez, Christopher Kaiser-Bunbury, Serguei Saavedra.

## Installation

You can install the development version of ReproduceRapidMonitoring from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("clsong/ReproduceRapidMonitoring")
```

## Reproduce
The main figures can be reproduced simply by running the corresponding functions. For example, figure 3B can be reproduced as
```{r dpi=300, warning=F, message=F}
library(ReproduceRapidMonitoring)
generate_figure3B_plot()
```

