---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ReproduceMetaCap

<!-- badges: start -->
<!-- badges: end -->

The goal of this package is to reproduce the paper “Rapid monitoring for ecological persistence” by Chuliang Song, Benno Simmons, Marie-Josée Fortin, Andrew Gonzalez, Christopher Kaiser-Bunbury, and Serguei Saavedra. A preprint of this paper can be found on BiorXiv ([link](https://www.biorxiv.org/content/10.1101/2022.07.02.498308v1)).


## Installation

You can install the development version of ReproduceRapidMonitoring from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("clsong/ReproduceRapidMonitoring")
```

## Reproduce
The main figures can be reproduced simply by running *plot_figure_Number*. For example, figure 3 can be reproduced as
```{r dpi=300, warning=F, message=F}
library(ReproduceMetaCap)
plot_figure_3B()
```
